---
title: "my first rmarkdown"
author: "noor"
date: "12/21/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Hello
## Tada
### R Markdown
- This  
- is  
- bullets
This is an **R Markdown** *document*. Markdown is   a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

~~strikethrough~~


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
```
```{r print}
print("Hello World")
```
```{r}
print("Hello World")
```
```{r}
print("Comes om second page")
```




```{r}
```


```{r}
```
```{r}
print("Lets try this")
```

